A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss from Powdery Mildew in Australian Mungbean

### 2020-08-07 paper/paper.Rmd
Edits for flow

The disease cycle of the pathogen can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, which disseminate to new infection sites [@PerezGarcia2009; @Sparks2017].
Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
To date, the sexual cycle that produces chasomthecia has not been observed in Australian mungbean.
And while the powdery mildew pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified in Australia.

>>>>

The disease cycle of the pathogen can be as short as five days for a germinating conidia to infect the host and produce new reproductive structures, conidiophores, which produce more conidia, and which then disseminate to new infection sites [@PerezGarcia2009; @Sparks2017].
Weather conditions that favour the rapid development of the disease are cool temperatures between 22&nbsp;&deg; and 26&nbsp;&deg;C, and a leaf surface that is not overly wet for infection [@Kelly2017a].
To date, the sexual cycle that produces chasomthecia has not been observed in Australian mungbean.
And while the powdery mildew pathogens are obligate parasites, secondary hosts that allow the pathogens to over-season between mungbean crops have not yet been identified in Australia.
